### 2019-01-13 papers/journal/qbf-table.tex
Experimentation 0.1 version
Added Biological Interpretation to the REsult section
Universal condition table restructure
Fancy table everywhere

\begin{table}[t]
	\centering
	    \def\arraystretch{1.1}
%	\caption{{\bf SAT and QBF implementation comparison.}}
%	\adjustbox{max height=\dimexpr\textheight-5.5cm\relax,
%		max width=\textwidth}{
		\begin{tabular}[t]{|c|c|c|c|c|c|}\hline

			{\multirow{2}{*} {Sr.No}}  & \multicolumn{2}{c|}{Regulation} & \multicolumn{3}{c|}{Universal condition}

		%	\\\cline{2-7}

%			{} & \multicolumn{2}{c|}{\textbf{2-connected} } & \multicolumn{2}{c|}{\textbf{3-connected} } & \multicolumn{2}{c|}{\textbf{2-connected}}  &  \multicolumn{2}{c|}{\textbf{4-connected}}

			%{} & \multicolumn{2}{c|}{2-connected} & \multicolumn{2}{c|}{3-connected} & \multicolumn{2}{c|}{2-connected}  &  \multicolumn{2}{c|}{4-connected}

			\\\cline{2-6}
			{} & {Node} & {Edge} & {Connectivity} & {SAT-time} & {QBF-time}

			\\\hline
			1. & Bf & Bf & 3C & 2.12 & 1.89  \\\hline
			2. & None & Bf  & 3C & 7.12 & 4.89  \\\hline
			3. & Bf & SNARE inhib & 4C  & M/O & 7.66 \\\hline
			4. & None & SNARE inhib  & No graph & M/O & 48.35 \\\hline
			5. & Bf & None  & No graphs & M/O & 890.84 \\\hline
			6. &  None & None  & No graphs & M/O & M/O \\\hline

	\end{tabular}
%}
	\caption{ SAT and QBF implementation comparison (in secs.)}
	\label{tab:satqbf-graph}
\end{table}

>>>>

\begin{table}[t]
	\centering
	\def\arraystretch{1.2}
%	\begin{tabular}{ c|c|c|c }
%		\hline
%		{\multirow{2}{*}{Variant}}  &
%		\multicolumn{2}{c|} {Constraints} & 
%		%	{\multirow{2}{*}{\textbf{Results}}}
%		{\multirow{2}{*}{Graph connectivity }} 
%		\\
%		\cline{2-3}
%		&  Rest & Activity & 
%		\\ \hline
%		
%		A. & \multirow{5}{*}{
%			\makecell{ \texttt{Consistancy}, \\  \texttt{Stability}, \\
%				 \texttt{Connected(k)}  }
%		}
%		& \ref{eq:ann},\ref{eq:aen} & No graph   \\
%		B. & & \ref{eq:anb},\ref{eq:aen} & No graph \\
%		C. & & \ref{eq:ann},\ref{eq:aeb} & 3-connected \\
%		D. & & \ref{eq:anb},\ref{eq:aeb} & 3-connected \\
%		E. & & \ref{eq:ann},\ref{eq:aep} & No graph    \\
%		F. & & \ref{eq:anb},\ref{eq:aep} & 4-connected \\\hline
%		
%		% C_es :Self edges are allowed
%		% C_ed : Every edge is distinct 
%	\end{tabular}
	\begin{tabular}{ c|c c c|c }
	\hline
	{\multirow{3}{*}{Variant}}  &
	\multicolumn{3}{c|} {Constraints} & 
	%	{\multirow{2}{*}{\textbf{Results}}}
	{\multirow{3}{*}{Graph connectivity} } 
	\\
	\cline{2-4}
	& 	{\multirow{2}{*}{Rest} }  & 	\multicolumn{2}{c|} {Activity} & 
	\\ 
	\cline{3-4}
	&  & Node  & Edge & 
	\\\hline

	A. & \multirow{5}{*}{
					\makecell{ \texttt{Consistancy}, \\  \texttt{Stability}, \\
						 \texttt{Connected(k)}  }
	}
	& \ref{eq:ann} & \ref{eq:aen} & No graph  \\
	B. & & \ref{eq:anb} & \ref{eq:aen} & No graph \\
	C. & & \ref{eq:ann} &  \ref{eq:aeb} &  3-connected \\
	D. & & \ref{eq:anb} & \ref{eq:aeb} & 3-connected \\
	E. & & \ref{eq:ann} & \ref{eq:aep} & No graph  \\
	F. & & \ref{eq:anb} &  \ref{eq:aep} & 4-connected \\\hline

	% C_es :Self edges are allowed
	% C_ed : Every edge is distinct 
\end{tabular}
	\caption{ QBF result for graph connectivity}
	\label{tab:qbf-graph}
\end{table}
